\begin{center}
    \textbf{Projects}
\end{center}

% PlayStation Games Analysis
\textbf{PlayStation Games Analysis. Lead Analyst} \hfill Remote | May 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Conducted data scraping and analysis of games on the PlayStation Store website
    \item Trained a predictive model using Gradient Boosting to forecast game ratings
    \item Optimized model performance with GridSearchCV, achieving high prediction accuracy
    \item Implemented A/B testing to evaluate and refine model predictions
\end{itemize}

% Android app development
\textbf{Android app development. Summer internship at the university} \hfill Remote | Jul 2023 – Aug 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed an Android application using Kotlin
    \item Studied Kotlin programming language and Android SDK
    \item Created a simple game as a sample application
    \item Successfully presented and defended the developed application
\end{itemize}

% Exploring the impact of technology on society
\textbf{Exploring the impact of technology on society. Coursework} \hfill Moscow, Russia | Sep 2023 – May 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Analyzed 210,000 news articles using NLP techniques.
    \item Developed predictive models for societal technology impact.
    \item Evaluated economic, educational, and healthcare tech transformations.
    \item Proposed ethical frameworks for technology implementation.
\end{itemize}

% Search for potential Jews among members of VK groups
\textbf{Search for potential Jews among members of VK groups. Lead Analyst} \hfill Moscow, Russia | Sep 2024
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item I collected data on the participants of VK groups dedicated to HSE
    \item After the collection, I analyzed on a variety of parameters whether this person can be a potential member of the Jewish club of HSE or not.
\end{itemize}